\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[a4paper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

\begin{document}
\hfill Jan Romanovský
\begin{center}
    \textbf{The Melos madness}
\end{center}


Every day I'm walking down the street, I've got places to be, and every day, without fault, I'm stopped by another wailing orator screaming: "Spare the Melians! What have they ever done to us?" I get it. \underline{Until recently, our relations have been neutral, if not amicable.} (6/3) Well I'll tell you what's happening right now -- if you haven't \underline{ascertained} (1) it yet -- we're at war.

War is a dog-eat-dog situation. You either win big-time or lose big-time. Entire societies are reduced to primitive hiveminds \underline{resolved} only \underline{to} (5) survive. In this \underline{undertaking} (3), it is only logical, that you shall do \textit{anything} to come out on top. In war there are no laws nor judges to enforce them. There is only power, and those strong enough to wield it such that it is not their land, but their enemies' being plundered and not their wives and chlidren, but their enemies' being sold into slavery.

That is exactly our situation. \underline{If it weren't Athens sieging Melos it would be Sparta sieging} \underline{Athens, or if not Athens} \underline{per se} (4), \underline{certainly one of her allies.} (7/8) Such is the natural state of affairs -- do you weep every single sheep and pig and hen you slaughter just to keep yourself fed? Of course you don't.

Melos is the hen and we have to slaughter it. Stop getting so \underline{unnerved} (2) by it.
\end{document}
