\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[a4paper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

\begin{document}
\hfill Jan Romanovský
\begin{center}
    \textbf{Proxenus, please!}
\end{center}


What everyone thinks of first when talking about generals is battle. The leader making critical strategic decisions in the heat of the moment. How the history might have changed \underline{were} the general \underline{to have decided} (4) differently. \underline{It is only as you start looking deeper that} (1) you find the true daily bread of the ancient army -- most of the time is spent marching and preparing. That's why I would like Proxenus, please!

Imagine having to spend months or years away. Away from home, family, friends, etc. You would be looking to make your stay as pleasant as possible. That would be an \underline{exericise in futility}~(3) having a harsh general \underline{reproaching you} (9) for your every mistake or minor sign of disobedience or lack of discipline. Probably even more so having one ready to sell you out to the highest bidder, regardless of your fate. Proxenus, on the other hand, leads benevolently but firmly. He has some \underline{inherent}~(7) compassion for his fellow soldiers and knows how to reward hard work and above all~--~honesty and justness.

War is \underline{ultimately} (5) a horrible occurence. When a man comes out of war with his life and honor intact he becomes the true winner. Surviving without compromising your morals in the inhospitable environments torn by war is, in my eyes, the quality of a true leader. A quality which Proxenus possesses. \underline{Thus}, with all \underline{that said} (2), \underline{it will be} quite \underline{unsurprising} to you \underline{that} (8), \underline{for my part} (6), I would prefer to serve under Proxenus.

\end{document}
