% soctepmlate unofficial - SOČ = Středoškolská odborná činnost - Czech competition
% Author: Vojtěch Boček
% Edit by: Jaroslav Páral
% Version: 2018-02-12
% Source code: https://github.com/RoboticsBrno/soctemplate/
% Base on: http://www.jcmm.cz/cz/sablona-soc.html
% License: CC BY 4.0

\documentclass{template/socthesis}

\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{mhchem}

\addbibresource{text.bib}
\graphicspath{{images/}}

\titlecz{Chemické pokusy}
\titleen{Chemical experiments}
\author{Jan Romanovský}
\field{12}
\school{Gymnázium Brno, třída Kpt.~Jaroše}
\mentor{Mgr. Zdeněk Moravec, Ph.D., a Mgr. et Mgr. Zuzana Plavčanová, Ph.D.}
\mentorstatement{Mgr. Zdeňka Moravce, Ph.D., a Mgr. et Mgr. Zuzany Plavčanové, Ph.D.,}

% Změňte, pokud se liší
%\region{Jihomoravský}
%\placefooter{Brno 2024}

\begin{document}

	\maketitle

	\makecopyrightstatement{V~Brně}

	\pagestyle{empty}

	\section*{Anotace}
	Cílem práce je pojednání o důležitosti chemických pokusů v moderní výuce chemie, dále tvorba lehce přístupného katalogu efektních chemických pokusů, který by sloužil jako pomůcka při výuce chemie na ZŠ a SŠ. Práce je členěna do teoretické a praktické části, dále do podcelků podle logické návaznosti k tématu textu.
	Cílem teoretické části je podat shrnutou historii výuky chemie v ČR, vymezit chemické pokusy jako pomůcku při výuce chemie a popsat význam chemických pokusů ve výuce.
	Cílem praktické části je provedení několika pokusů a jejich následné zpracování do katalogu pro potřeby výuky na ZŠ a SŠ.

	\subsection*{Klíčová slova}
	chemický pokus, výuka chemie

	\vspace{20mm}

	\section*{Annotation}
	The goal of this paper is a discourse on the importance of chemical experiments in chemistry education and the creation of an easily available catalogue of simple chemical experiments that would serve as a tool for teaching chemistry at elementary and high schools. The paper is divided into a theoretical and a practical section, then into subsections according to the relation to the topic of the text.
	The goal of the theoretical section is to tell a concise history of chemistry education in Czechia, to define a chemical experiment as a tool in teaching chemistry, and to describe the importance of chemical experiments in teaching chemistry.
	The goal of the practical section is the reproduction of a few chemical experiments and their cataloguing for the needs of chemistry education at elementary and high schools.

	\subsection*{Keywords}
	chemical experiment, chemistry teaching

	\newpage
	\pagestyle{plain}

    \tableofcontents % vysází obsah

	%%% Začátek práce
	\setcounter{figure}{0}
	\setcounter{table}{0}
	\newpage

	%%% Vložení jednotlivých částí
	\input{text-01-uvod.tex}

	\input{text-02-teoreticka-cast.tex}

	\input{text-03-prakticka-cast.tex}

	\input{text-04-zaver.tex}

	\newpage
	\printbibliography[title=Literatura]
	\addcontentsline{toc}{chapter}{Literatura}

	\listoffigures
	\addcontentsline{toc}{chapter}{Seznam obrázků}

	%%%\listoftables
	%%%\addcontentsline{toc}{section}{Seznam tabulek}

	%%%\listoflistedequation
	%%%\addcontentsline{toc}{section}{Seznam rovnic}

\end{document}
